Response to reviewers and editorial comments for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2023-01-31 src/docs_review/review.Rmd
Add line numbers for changed review text

The reviewer is right to note that multinomial logistic regression models can be implemented in probabilistic programming languages like `WinBUGS` directly.
However, for this application, Markov chain Monte Carlo approaches would be prohibitively expensive.
For this reason, we chose to use integrated nested Laplace approximations via `R-INLA`, which have been shown to have comparable accuracy for latent Gaussian models in the realistic, pre-asymptotic regime.
We have added the following text to the methods section of the manuscript to clarify this point:

> For models with a Gaussian latent field, INLA has comparable accuracy to Markov chain Monte Carlo in the realistic, pre-asymptotic regime, and is substantially more computationally tractable for high dimensional models like ours, which has 940 districts, 20 years, 3 age groups, and 4 risk groups.

@@

We agree that identifying predictive and measurable predictors of risk group proportions, or high risk locations, is an important area for further research.
We have commented on this in the discussion section:

@@

Thank you to the reviewer for highlighting the omission of specific definition for this term.
Throughout the manuscript, we have replaced references to "effect" by the more accurate "random effect", and have clarified the usage of spatial random effect where it first appears in the methods section as follows:

@@

Overall, we agree with the reviewer's comment that relying on data from different designs is not the ideal analysis, but we believe that it is the best approach using available data given known limitations identifying women who sell sex in household sampling frames and questionnaires.
We have noted this in the limitations section of the discussion:

@@

In our and other previous work, figures similar to Figure 1 have been effective at concisely visualising inclusion of a large number of surveys across several countries and types (see, for example, Figure 1 of @giguere2021trends), and we prefer to retain this figure.
Supplementary Table B.3 provides an alternative tabular summary of the surveys analysed, with sample size broken down by age group. 
We have extended the caption of Figure 1 to draw attention to this alternative presentation:

>>>>

The reviewer is right to note that multinomial logistic regression models can be implemented in probabilistic programming languages like `WinBUGS` directly.
However, for this application, Markov chain Monte Carlo approaches would be prohibitively expensive.
For this reason, we chose to use integrated nested Laplace approximations via `R-INLA`, which have been shown to have comparable accuracy for latent Gaussian models in the realistic, pre-asymptotic regime.
We have added the following text to the methods section of the manuscript (lines 126-129) to clarify this point:

> For models with a Gaussian latent field, INLA has comparable accuracy to Markov chain Monte Carlo with realistic, finite samples, and is substantially more computationally tractable for high dimensional models like ours, which has 940 districts, 20 years, 3 age groups, and 4 risk groups.

@@

We agree that identifying predictive and measurable predictors of risk group proportions, or high risk locations, is an important area for further research.
We have commented on this in the discussion section (lines 316-321):

@@

Thank you to the reviewer for highlighting the omission of specific definition for this term.
Throughout the manuscript, we have replaced references to "effect" by the more accurate "random effect", and have clarified the usage of the term spatial random effect where it first appears in the methods section (lines 108-114) as follows:

@@

Overall, we agree with the reviewer's comment that relying on data from different designs is not the ideal analysis, but we believe that it is the best approach using available data given known limitations identifying women who sell sex in household sampling frames and questionnaires.
We have noted this in the limitations section of the discussion (lines 311-316):

@@

In our and other previous work, figures similar to Figure 1 have been effective at concisely visualising inclusion of a large number of surveys across several countries and types (see, for example, Figure 1 of @giguere2021trends), and we prefer to retain this figure.
Supplementary Table B.3 provides an alternative tabular summary of the surveys analysed, with sample size broken down by age group. 
We have extended the caption of Figure 1 (proceeding line 170) to draw attention to this alternative presentation:
